SpARC: Sparse Redundant Calibration

### 2016-07-15 paper.tex
newest paper version

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand{\bz}{\bmath{z}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\conj}[1]{\overline{#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared
\newcommand{\bz}{\bmath{z}}
\newcommand{\br}{\bmath{r}}
\newcommand{\bg}{\bmath{g}}
\newcommand{\bd}{\bmath{d}}
\newcommand{\bv}{\bmath{v}}
\newcommand{\by}{\bmath{y}}
\newcommand{\conj}[1]{\overline{#1}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Redundant calibration}
In the case of a redundant array we can not only solve for the gains $\bg$ but also the redundant visibilities $\by$ themselves. Where $\by = [y_1,\cdots,y_R]$, $y_i$ denotes 
a unique redundant visibility and $R$ is the maximum value of the mapping $\phi_{ij}$. The reason we can now also solve for $\by$ is because we have reduced the number of 
unknowns from $N+B$ to $N+R$, where $N+R$ is now less than $B$ due to the array redundancy. We can now reformulate the calibration problem for an redundant array as follow:
\begin{equation}
\min_{\bz}\|\br\| = \min_{\bz}\|\bd - \bv(\bz)\|, 
\end{equation}
where $\bz = [\bg,\by]^T$.
